---
title: "Client Incident Reports: Jan 2016 - June 2016"
author: "Evan Harley"
date: "7 August 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
  word_document: default
header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{graphicx}
mainfont: Calibri
---
\pagestyle{fancyplain}
\fancyhf{}
\fancyhead[L]{\includegraphics[width=\textwidth,height=1.0cm]{logo1.png}}
\fancyhead[CR]{\includegraphics[width=\textwidth,height=1.0cm]{logo2.png}}


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(scales)
library(knitr)

setwd('C:/Users/Evan/PycharmProjects/Paladin_Analysis')
data <- read.csv("Thrifty Foods_1_half_2016.csv")

data$inc_date <- paste(data$Date, data$Month, data$Year, sep= '/')

data$inc_date <- as.Date(data$inc_date, format = "%d/%B/%Y")
data$Day.of.Week <- weekdays(data$inc_date)

```

#Introduction

This report is an Analysis of Paladin Security's incident report data for the Client chain of sites, from January to June 2016. The intent of the analysis is to highlight any trends that might be found in the data, in hopes of increasing the quality of the service we offer. This includes any potential issues, and areas of concern that may exist. 

This is a rather small data set, having 268 observations. The data set is also skewed heavily, in that one Site, J, makes up 35.44% of the total observations. In this report I have presented each Site's report data separately, to mitigate this skew as much as possible.

The first section of the report consists of general statistics. The plots in this section will have the data for J removed to mitigate the skew that it causes. The second section contains plots which explore show each Site's data separate from the rest of the data. 

As data analysis is a question driven process, any questions that you have which are not answered in the report likely can be, feel free to forward any requests for more detail or analysis to me. 
\newpage

#General Statistics

##Statistical Values

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

cat(paste("Total number of Incidents Reported: ", nrow(data)))
```
\newline
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat(paste("Average Number of Incidents Reported per month: ", (nrow(data)/6)))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
Site_data <- tally(group_by(data, Site), sort = T)
Site_data$percentage <- (Site_data$n/nrow(data)) * 100
Site_data$average_per_month <- (Site_data$n/6)
table = kable(Site_data, caption="Report Data broken by Site")
cat(table, sep = '\n')
rm(Site_data)
rm(table)
```

##General Plots

The following plots have had the data for J removed to minimize the skew in the data caused by it being the Site generating the most reports.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
gen_data <- data[data$Site != "J", ]

gen_month <- tally(group_by(gen_data, Month), sort = T)
gen_month$percentage <- (gen_month$n/nrow(gen_data))*100
avg_month <- mean(gen_month$percentage)
sd_month <- sd(gen_month$percentage)

ggplot(aes(x = Month, y = percentage), data = gen_month)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("January","February","March", "April","May", "June", "July", "August", "September", "October", "November", "December"))+
  geom_hline(yintercept= avg_month, colour= "blue") +
  geom_hline(yintercept= avg_month + sd_month, colour = "darkred") +
  geom_hline(yintercept= avg_month - sd_month, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Month")
rm(gen_month)
rm(avg_month)
rm(sd_month)

gen_dow <- tally(group_by(gen_data, Day.of.Week), sort = T)
gen_dow$percentage <- (gen_dow$n/nrow(gen_data))*100
avg_dow <- mean(gen_dow$percentage)
sd_dow <- sd(gen_dow$percentage)

ggplot(aes(x = Day.of.Week, y = percentage), data = gen_dow)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))+
  geom_hline(yintercept= avg_dow, colour= "blue") +
  geom_hline(yintercept= avg_dow + sd_dow, colour = "darkred") +
  geom_hline(yintercept= avg_dow - sd_dow, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Day of the Week")
rm(gen_dow)
rm(sd_dow)
rm(avg_dow)
```
\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.width=3.5}
gen_hour <- tally(group_by(gen_data, Hour), sort = T)
gen_hour$percentage <- (gen_hour$n/nrow(gen_data))*100
avg_hour <- mean(gen_hour$percentage)
sd_hour <- sd(gen_hour$percentage)

ggplot(aes(x=Hour, y=percentage), data = transform(gen_hour,
                                Hour = factor(Hour,                                                   levels = c(21,22,23,0,1,2,3,4,5,6,7))))+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete() +
  geom_hline(yintercept= avg_hour, colour= "blue") +
  geom_hline(yintercept= avg_hour + sd_hour, colour = "darkred") +
  geom_hline(yintercept= avg_hour - sd_hour, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Hour of Shift")

rm(avg_hour)
rm(sd_hour)
rm(gen_hour)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
gen_type <- tally(group_by(gen_data, Type.of.Incident), sort = T)
gen_type$percentage <- (gen_type$n/nrow(gen_data))*100
gen_type <- head(gen_type, 10)
avg_type <- mean(gen_type$percentage)
sd_type <- sd(gen_type$percentage)

ggplot(aes(x = Type.of.Incident, y = percentage), data = gen_type)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  geom_hline(yintercept= avg_type, colour= "blue") +
  geom_hline(yintercept= avg_type + sd_type, colour = "red") +
  geom_hline(yintercept= avg_type + (2 * sd_type), colour = "darkred") +
  geom_hline(yintercept= avg_type - sd_type, colour = "red") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Type")
```

#Site Specific Plots

##J

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
gen_data <- data[data$Site == "J", ]

gen_month <- tally(group_by(gen_data, Month), sort = T)
gen_month$percentage <- (gen_month$n/nrow(gen_data))*100
avg_month <- mean(gen_month$percentage)
sd_month <- sd(gen_month$percentage)

ggplot(aes(x = Month, y = percentage), data = gen_month)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("January","February","March", "April","May", "June", "July", "August", "September", "October", "November", "December"))+
  geom_hline(yintercept= avg_month, colour= "blue") +
  geom_hline(yintercept= avg_month + sd_month, colour = "darkred") +
  geom_hline(yintercept= avg_month - sd_month, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Month")
rm(gen_month)
rm(avg_month)
rm(sd_month)

gen_dow <- tally(group_by(gen_data, Day.of.Week), sort = T)
gen_dow$percentage <- (gen_dow$n/nrow(gen_data))*100
avg_dow <- mean(gen_dow$percentage)
sd_dow <- sd(gen_dow$percentage)

ggplot(aes(x = Day.of.Week, y = percentage), data = gen_dow)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))+
  geom_hline(yintercept= avg_dow, colour= "blue") +
  geom_hline(yintercept= avg_dow + sd_dow, colour = "darkred") +
  geom_hline(yintercept= avg_dow - sd_dow, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Day of the Week")
rm(gen_dow)
rm(sd_dow)
rm(avg_dow)

gen_hour <- tally(group_by(gen_data, Hour), sort = T)
gen_hour$percentage <- (gen_hour$n/nrow(gen_data))*100
avg_hour <- mean(gen_hour$percentage)
sd_hour <- sd(gen_hour$percentage)

ggplot(aes(x=Hour, y=percentage), data = transform(gen_hour,
                                Hour = factor(Hour,                                                   levels = c(21,22,23,0,1,2,3,4,5,6,7))))+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete() +
  geom_hline(yintercept= avg_hour, colour= "blue") +
  geom_hline(yintercept= avg_hour + sd_hour, colour = "darkred") +
  geom_hline(yintercept= avg_hour - sd_hour, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Hour of Shift")

rm(avg_hour)
rm(sd_hour)
rm(gen_hour)

gen_type <- tally(group_by(gen_data, Type.of.Incident), sort = T)
gen_type$percentage <- (gen_type$n/nrow(gen_data))*100
gen_type <- head(gen_type, 10)
avg_type <- mean(gen_type$percentage)
sd_type <- sd(gen_type$percentage)

ggplot(aes(x = Type.of.Incident, y = percentage), data = gen_type)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  geom_hline(yintercept= avg_type, colour= "blue") +
  geom_hline(yintercept= avg_type + sd_type, colour = "red") +
  geom_hline(yintercept= avg_type + (2 * sd_type), colour = "darkred") +
  geom_hline(yintercept= avg_type - sd_type, colour = "red") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Type")
```

##T

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
gen_data <- data[data$Site == "T", ]

gen_month <- tally(group_by(gen_data, Month), sort = T)
gen_month$percentage <- (gen_month$n/nrow(gen_data))*100
avg_month <- mean(gen_month$percentage)
sd_month <- sd(gen_month$percentage)

ggplot(aes(x = Month, y = percentage), data = gen_month)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("January","February","March", "April","May", "June", "July", "August", "September", "October", "November", "December"))+
  geom_hline(yintercept= avg_month, colour= "blue") +
  geom_hline(yintercept= avg_month + sd_month, colour = "darkred") +
  geom_hline(yintercept= avg_month - sd_month, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Month")
rm(gen_month)
rm(avg_month)
rm(sd_month)

gen_dow <- tally(group_by(gen_data, Day.of.Week), sort = T)
gen_dow$percentage <- (gen_dow$n/nrow(gen_data))*100
avg_dow <- mean(gen_dow$percentage)
sd_dow <- sd(gen_dow$percentage)

ggplot(aes(x = Day.of.Week, y = percentage), data = gen_dow)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))+
  geom_hline(yintercept= avg_dow, colour= "blue") +
  geom_hline(yintercept= avg_dow + sd_dow, colour = "darkred") +
  geom_hline(yintercept= avg_dow - sd_dow, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Day of the Week")
rm(gen_dow)
rm(sd_dow)
rm(avg_dow)

gen_hour <- tally(group_by(gen_data, Hour), sort = T)
gen_hour$percentage <- (gen_hour$n/nrow(gen_data))*100
avg_hour <- mean(gen_hour$percentage)
sd_hour <- sd(gen_hour$percentage)

ggplot(aes(x=Hour, y=percentage), data = transform(gen_hour,
                                Hour = factor(Hour,                                                   levels = c(21,22,23,0,1,2,3,4,5,6,7))))+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete() +
  geom_hline(yintercept= avg_hour, colour= "blue") +
  geom_hline(yintercept= avg_hour + sd_hour, colour = "darkred") +
  geom_hline(yintercept= avg_hour - sd_hour, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Hour of Shift")

rm(avg_hour)
rm(sd_hour)
rm(gen_hour)

gen_type <- tally(group_by(gen_data, Type.of.Incident), sort = T)
gen_type$percentage <- (gen_type$n/nrow(gen_data))*100
gen_type <- head(gen_type, 10)
avg_type <- mean(gen_type$percentage)
sd_type <- sd(gen_type$percentage)

ggplot(aes(x = Type.of.Incident, y = percentage), data = gen_type)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  geom_hline(yintercept= avg_type, colour= "blue") +
  geom_hline(yintercept= avg_type + sd_type, colour = "red") +
  geom_hline(yintercept= avg_type + (2 * sd_type), colour = "darkred") +
  geom_hline(yintercept= avg_type - sd_type, colour = "red") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Type")
```

##CW
``````{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
gen_data <- data[data$Site == "CW", ]

gen_month <- tally(group_by(gen_data, Month), sort = T)
gen_month$percentage <- (gen_month$n/nrow(gen_data))*100
avg_month <- mean(gen_month$percentage)
sd_month <- sd(gen_month$percentage)

ggplot(aes(x = Month, y = percentage), data = gen_month)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("January","February","March", "April","May", "June", "July", "August", "September", "October", "November", "December"))+
  geom_hline(yintercept= avg_month, colour= "blue") +
  geom_hline(yintercept= avg_month + sd_month, colour = "darkred") +
  geom_hline(yintercept= avg_month - sd_month, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Month")
rm(gen_month)
rm(avg_month)
rm(sd_month)

gen_dow <- tally(group_by(gen_data, Day.of.Week), sort = T)
gen_dow$percentage <- (gen_dow$n/nrow(gen_data))*100
avg_dow <- mean(gen_dow$percentage)
sd_dow <- sd(gen_dow$percentage)

ggplot(aes(x = Day.of.Week, y = percentage), data = gen_dow)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))+
  geom_hline(yintercept= avg_dow, colour= "blue") +
  geom_hline(yintercept= avg_dow + sd_dow, colour = "darkred") +
  geom_hline(yintercept= avg_dow - sd_dow, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Day of the Week")
rm(gen_dow)
rm(sd_dow)
rm(avg_dow)

gen_hour <- tally(group_by(gen_data, Hour), sort = T)
gen_hour$percentage <- (gen_hour$n/nrow(gen_data))*100
avg_hour <- mean(gen_hour$percentage)
sd_hour <- sd(gen_hour$percentage)

ggplot(aes(x=Hour, y=percentage), data = transform(gen_hour,
                                Hour = factor(Hour,                                                   levels = c(21,22,23,0,1,2,3,4,5,6,7))))+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete() +
  geom_hline(yintercept= avg_hour, colour= "blue") +
  geom_hline(yintercept= avg_hour + sd_hour, colour = "darkred") +
  geom_hline(yintercept= avg_hour - sd_hour, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Hour of Shift")

rm(avg_hour)
rm(sd_hour)
rm(gen_hour)

gen_type <- tally(group_by(gen_data, Type.of.Incident), sort = T)
gen_type$percentage <- (gen_type$n/nrow(gen_data))*100
gen_type <- head(gen_type, 10)
avg_type <- mean(gen_type$percentage)
sd_type <- sd(gen_type$percentage)

ggplot(aes(x = Type.of.Incident, y = percentage), data = gen_type)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  geom_hline(yintercept= avg_type, colour= "blue") +
  geom_hline(yintercept= avg_type + sd_type, colour = "red") +
  geom_hline(yintercept= avg_type + (2 * sd_type), colour = "darkred") +
  geom_hline(yintercept= avg_type - sd_type, colour = "red") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Type")
```

##CD

``````{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
gen_data <- data[data$Site == "CD", ]

gen_month <- tally(group_by(gen_data, Month), sort = T)
gen_month$percentage <- (gen_month$n/nrow(gen_data))*100
avg_month <- mean(gen_month$percentage)
sd_month <- sd(gen_month$percentage)

ggplot(aes(x = Month, y = percentage), data = gen_month)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("January","February","March", "April","May", "June", "July", "August", "September", "October", "November", "December"))+
  geom_hline(yintercept= avg_month, colour= "blue") +
  geom_hline(yintercept= avg_month + sd_month, colour = "darkred") +
  geom_hline(yintercept= avg_month - sd_month, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Month")
rm(gen_month)
rm(avg_month)
rm(sd_month)

gen_dow <- tally(group_by(gen_data, Day.of.Week), sort = T)
gen_dow$percentage <- (gen_dow$n/nrow(gen_data))*100
avg_dow <- mean(gen_dow$percentage)
sd_dow <- sd(gen_dow$percentage)

ggplot(aes(x = Day.of.Week, y = percentage), data = gen_dow)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))+
  geom_hline(yintercept= avg_dow, colour= "blue") +
  geom_hline(yintercept= avg_dow + sd_dow, colour = "darkred") +
  geom_hline(yintercept= avg_dow - sd_dow, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Day of the Week")
rm(gen_dow)
rm(sd_dow)
rm(avg_dow)

gen_hour <- tally(group_by(gen_data, Hour), sort = T)
gen_hour$percentage <- (gen_hour$n/nrow(gen_data))*100
avg_hour <- mean(gen_hour$percentage)
sd_hour <- sd(gen_hour$percentage)

ggplot(aes(x=Hour, y=percentage), data = transform(gen_hour,
                                Hour = factor(Hour,                                                   levels = c(21,22,23,0,1,2,3,4,5,6,7))))+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete() +
  geom_hline(yintercept= avg_hour, colour= "blue") +
  geom_hline(yintercept= avg_hour + sd_hour, colour = "darkred") +
  geom_hline(yintercept= avg_hour - sd_hour, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Hour of Shift")

rm(avg_hour)
rm(sd_hour)
rm(gen_hour)

gen_type <- tally(group_by(gen_data, Type.of.Incident), sort = T)
gen_type$percentage <- (gen_type$n/nrow(gen_data))*100
gen_type <- head(gen_type, 10)
avg_type <- mean(gen_type$percentage)
sd_type <- sd(gen_type$percentage)

ggplot(aes(x = Type.of.Incident, y = percentage), data = gen_type)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  geom_hline(yintercept= avg_type, colour= "blue") +
  geom_hline(yintercept= avg_type + sd_type, colour = "red") +
  geom_hline(yintercept= avg_type + (2 * sd_type), colour = "darkred") +
  geom_hline(yintercept= avg_type - sd_type, colour = "red") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Type")
```

##B

`````````{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
gen_data <- data[data$Site == "B", ]

gen_month <- tally(group_by(gen_data, Month), sort = T)
gen_month$percentage <- (gen_month$n/nrow(gen_data))*100
avg_month <- mean(gen_month$percentage)
sd_month <- sd(gen_month$percentage)

ggplot(aes(x = Month, y = percentage), data = gen_month)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("January","February","March", "April","May", "June", "July", "August", "September", "October", "November", "December"))+
  geom_hline(yintercept= avg_month, colour= "blue") +
  geom_hline(yintercept= avg_month + sd_month, colour = "darkred") +
  geom_hline(yintercept= avg_month - sd_month, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Month")
rm(gen_month)
rm(avg_month)
rm(sd_month)

gen_dow <- tally(group_by(gen_data, Day.of.Week), sort = T)
gen_dow$percentage <- (gen_dow$n/nrow(gen_data))*100
avg_dow <- mean(gen_dow$percentage)
sd_dow <- sd(gen_dow$percentage)

ggplot(aes(x = Day.of.Week, y = percentage), data = gen_dow)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete(lim = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))+
  geom_hline(yintercept= avg_dow, colour= "blue") +
  geom_hline(yintercept= avg_dow + sd_dow, colour = "darkred") +
  geom_hline(yintercept= avg_dow - sd_dow, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Day of the Week")
rm(gen_dow)
rm(sd_dow)
rm(avg_dow)

gen_hour <- tally(group_by(gen_data, Hour), sort = T)
gen_hour$percentage <- (gen_hour$n/nrow(gen_data))*100
avg_hour <- mean(gen_hour$percentage)
sd_hour <- sd(gen_hour$percentage)

ggplot(aes(x=Hour, y=percentage), data = transform(gen_hour,
                                Hour = factor(Hour,                                                   levels = c(21,22,23,0,1,2,3,4,5,6,7))))+
  geom_bar(stat = "identity", fill = 'steelblue')+
  scale_x_discrete() +
  geom_hline(yintercept= avg_hour, colour= "blue") +
  geom_hline(yintercept= avg_hour + sd_hour, colour = "darkred") +
  geom_hline(yintercept= avg_hour - sd_hour, colour = "darkred") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Hour of Shift")

rm(avg_hour)
rm(sd_hour)
rm(gen_hour)

gen_type <- tally(group_by(gen_data, Type.of.Incident), sort = T)
gen_type$percentage <- (gen_type$n/nrow(gen_data))*100
gen_type <- head(gen_type, 10)
avg_type <- mean(gen_type$percentage)
sd_type <- sd(gen_type$percentage)

ggplot(aes(x = Type.of.Incident, y = percentage), data = gen_type)+
  geom_bar(stat = "identity", fill = 'steelblue')+
  geom_hline(yintercept= avg_type, colour= "blue") +
  geom_hline(yintercept= avg_type + sd_type, colour = "red") +
  geom_hline(yintercept= avg_type + (2 * sd_type), colour = "darkred") +
  geom_hline(yintercept= avg_type - sd_type, colour = "red") +
  theme(axis.text.x = element_text(angle=45))+
  ggtitle("Percent of Incidents by Type")
```